Trion ARPES signature

### 2024-01-04 paper/main.tex
update real space code
minor updates

We can define the canonical momenta of $\vb{r}_{1,2}$, 
hereafter referred to as $\vb{k}_{1,2}$, 
as $- \ii \hbar_{\vb{r}_{1, 2}}$;
in this way 
\begin{equation}
    \ke = \frac{\me}{M} \vb{P} - \vb{k}_1 - \vb{k}_2, \quad 
    \khi{1,2} = \vb{k}_{1, 2} + \frac{\mh}{M} \vb{P},
\end{equation}
and the kinetic energy part of the \eqref{eq:two-band-w} now reads 
\begin{equation}
    H_{\text{kin}} = \frac{(\vb{P} - \vb{w})^2}{2 M} + \Eg 
    + \frac{\vb{k}_1^2}{2\mh} + \frac{\vb{k}_2^2}{2\mh}
    - \frac{\vb{w}^2}{2M} + \frac{(\vb{k}_1 + \vb{k}_2 + \vb{w})^2}{2\me}.
\end{equation}
We however want to shift the definitions of $\vb{k}$ 
so that the kinetic part resembles the kinetic energy in a direct band gap system.
By redefining 
\begin{equation}
    \vb{k}_{1,2} = - \ii \hbar \vb{r}_{1, 2} + \frac{\vb{w}}{1 + \me / \mu}, \quad 
    \mu = \frac{\me \mh}{\me + \mh},
\end{equation}
and therefore 
\begin{equation}
    \ke = \frac{\me}{M} \vb{P} + \frac{2 \mh \vb{w}}{M} - \vb{k}_1 - \vb{k}_2, \quad 
    \khi{1,2} = \vb{k}_{1,2} - \frac{\mh \vb{w}}{M} + \frac{\mh}{M} \vb{P},
\end{equation}
the total Hamiltonian now reads
\begin{equation}
    H =  \frac{(\vb{P} - \vb{w})^2}{2 M} + \Eg 
    + \frac{\vb{k}_1^2}{2\mh} + \frac{\vb{k}_2^2}{2\mh} + \frac{\vb{k}_1 \cdot \vb{k}_2}{2\me}
    + V(\vb{r}_1 - \vb{r}_2) - V(\vb{r}_1) - V(\vb{r}_2).
\end{equation}
The redefinition of $\vb{k}_{1, 2}$ does not change the commutation relation 
between $\vb{r}_{1, 2}$ and $\vb{k}_{1, 2}$.
We find that the internal part of the Hamiltonian has the same form 
as the Hamiltonian in \cite{chang2021variationally}. 
This can also be seen as generalization of the indirect band gap exciton two-band model to the trion;
for the former we have \cite{rustagi2018photoemission} 
\begin{equation}
    H = \frac{(\vb{Q} - \vb{w})^2}{2M} + \Eg + \frac{\vb{k}^2}{2\mu} - V(\vb{r}), 
\end{equation}
where 
\begin{equation}
    M = \me + \me, \quad 
    \ke = \frac{\me}{M} \vb{Q} + \vb{k} + \frac{\mh}{M} \vb{w}, \quad 
    \kh = \frac{\mh}{M} \vb{Q} - \vb{k} - \frac{\mh}{M} \vb{w}.
\end{equation}

@@

@@

@@

Variational wave function: TODO list 
\begin{enumerate}
    \item We should work in the real space, because the form of $V$ can be complicated.
    \item The kinetic term should be evaluated analytically.
    \item Normalization??? Why the factor is $1 / \sqrt{2}$?
    \item The structure of the three-particle wave function.
\end{enumerate}

>>>>

We can define the canonical momenta of $\vb{r}_{1,2}$, 
hereafter referred to as $\vb{k}_{1,2}$, 
as $- \ii \hbar_{\vb{r}_{1, 2}}$;
in this way 
\begin{equation}
    \ke = \frac{\me}{M} \vb{P} - \vb{k}_1 - \vb{k}_2, \quad 
    \khi{1,2} = \vb{k}_{1, 2} + \frac{\mh}{M} \vb{P},
\end{equation}
and the kinetic energy part of the \eqref{eq:two-band-w} now reads 
\begin{equation}
    H_{\text{kin}} = \frac{(\vb{P} - \vb{w})^2}{2 M} + \Eg 
    + \frac{\vb{k}_1^2}{2\mh} + \frac{\vb{k}_2^2}{2\mh}
    - \frac{\vb{w}^2}{2M} + \frac{(\vb{k}_1 + \vb{k}_2 + \vb{w})^2}{2\me}.
\end{equation}
We however want to shift the definitions of $\vb{k}$ 
so that the kinetic part resembles the kinetic energy in a direct band gap system.
By redefining 
\begin{equation}
    \vb{k}_{1,2} = - \ii \hbar \vb{r}_{1, 2} + \frac{\vb{w}}{1 + \me / \mu}, \quad 
    \mu = \frac{\me \mh}{\me + \mh},
\end{equation}
and therefore 
\begin{equation}
    \ke = \frac{\me}{M} \vb{P} + \frac{2 \mh \vb{w}}{M} - \vb{k}_1 - \vb{k}_2, \quad 
    \khi{1,2} = \vb{k}_{1,2} - \frac{\mh \vb{w}}{M} + \frac{\mh}{M} \vb{P},
\end{equation}
the total Hamiltonian now reads
\begin{equation}
    H =  \frac{(\vb{P} - \vb{w})^2}{2 M} + \Eg +
    \underbrace{
        \frac{\vb{k}_1^2}{2\mh} + \frac{\vb{k}_2^2}{2\mh} + \frac{\vb{k}_1 \cdot \vb{k}_2}{2\me}
        + V(\vb{r}_1 - \vb{r}_2) - V(\vb{r}_1) - V(\vb{r}_2)
    }_{H_{\text{internal}}}.
\end{equation}
The redefinition of $\vb{k}_{1, 2}$ does not change the commutation relation 
between $\vb{r}_{1, 2}$ and $\vb{k}_{1, 2}$.
We find that the internal part of the Hamiltonian has the same form 
as the Hamiltonian in \cite{chang2021variationally}. 
This can also be seen as generalization of the indirect band gap exciton two-band model to the trion;
for the former we have \cite{rustagi2018photoemission} 
\begin{equation}
    H = \frac{(\vb{Q} - \vb{w})^2}{2M} + \Eg + \frac{\vb{k}^2}{2\mu} - V(\vb{r}), 
\end{equation}
where 
\begin{equation}
    M = \me + \me, \quad 
    \ke = \frac{\me}{M} \vb{Q} + \vb{k} + \frac{\mh}{M} \vb{w}, \quad 
    \kh = \frac{\mh}{M} \vb{Q} - \vb{k} - \frac{\mh}{M} \vb{w}.
\end{equation}

@@

The 3D version of the problem is solved in \cite{chandrasekhar1944some,hogaasen2010two};

@@

Serious problem:
\begin{equation}
    \int \dd[2]{\vb{r}_1} \int \dd[2]{\vb{r}_2} \ee^{- r_1 / a} \frac{1}{\abs*{\vb{r}_1 - \vb{r}_2}} \ee^{- r_2 / b}
\end{equation}
One option might be to numerically solve the interaction part, 
and use the analytic forms elsewhere.

@@

Variational wave function: TODO list 
\begin{enumerate}
    \item We should work in the real space, because the form of $V$ can be complicated.
    \item The kinetic term should be evaluated analytically.
    \item Normalization??? Why the factor is $1 / \sqrt{2}$?
    \item The structure of the three-particle wave function.
    \item Also see the paper Two-electron atoms, ions, and molecules http://users.df.uba.ar/dmitnik/estructura3/articulostrabajo/twoelectronatomsionsmolecules.pdf
    and https://articles.adsabs.harvard.edu/pdf/1944ApJ...100..176C
\end{enumerate}
